---
title: "p8105_hw1_cs3779"
author: "CJ Snyder"
date: "9/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Homework 1 - Problem 1
## Creating Data Frame
```{r}
hw_df = tibble(
  rand_var = rnorm(8),
  logic_vec = rand_var > 0,
  char_vec = as.character(logic_vec,8),
  fact_vec = factor(char_vec, 3)
  )

mean(pull(hw_df, rand_var))
mean(pull(hw_df, logic_vec))
mean(pull(hw_df, char_vec))
mean(pull(hw_df, fact_vec))
```

Trying to take the mean for _rand_var_ (numeric) and _logic_vec_ (logical) were both successful. The mean of _logic_vec_ might be the mean of the variables that came back TRUE if its value are greater than 0. 
Meanwhile, it was not possible to take the mean (i.e. came back as '**N/A**') for _char_vec_ or _fact_vec_ as they are both neither numeric nor logical. The only two types of variable that the mean function works on are numeric or logical.

### Dataframe Variable Conversion 
```{r, eval=FALSE}
# Converting logical vector to numeric
logic_to_numeric = as.numeric(hw_df$logic_vec)
prod_log_num = logic_to_numeric * (hw_df$rand_var)

# Converting logical vector to factor
logic_to_factor = as.factor(hw_df$logic_vec)
prod_log_fact = logic_to_factor * (hw_df$rand_var)

#Converting logical vector to factor then numeric
logic_factor_numeric = as.numeric(logic_to_factor)
prod_log_fact_num = logic_factor_numeric * (hw_df$rand_var)
```

Trying to take the means of the converted variables indicates that you can only take the mean of a numeric variable since the output for the mean of the _prod_log_fact_ variable was '**N/A**' - similar to above. 


