---
title: "p8105_hw1_cs3779"
author: "CJ Snyder"
date: "9/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Homework 1 - Problem 1
## Creating Dataframe _hw_df_
```{r}
hw_df = tibble(
  rand_var = rnorm(8),
  logic_vec = rand_var > 0,
  char_vec = as.character(logic_vec,8),
  fact_vec = factor(char_vec, 3)
  )

mean(pull(hw_df, rand_var))
mean(pull(hw_df, logic_vec))
mean(pull(hw_df, char_vec))
mean(pull(hw_df, fact_vec))
```

Trying to take the mean for _rand_var_ (numeric) and _logic_vec_ (logical) were both successful. The mean of _logic_vec_ might be the mean of the variables that came back **TRUE** if its value are greater than 0. 
Meanwhile, it was not possible to take the mean (i.e. came back as '**N/A**') for _char_vec_ or _fact_vec_ as they are both neither numeric nor logical. The only two types of variable that the mean function works on are numeric or logical.

### Dataframe _hw_df_ Variable Conversion 
```{r, eval=FALSE}
# Converting logical vector to numeric
logic_to_numeric = as.numeric(hw_df$logic_vec)
prod_log_num = logic_to_numeric * (hw_df$rand_var)

# Converting logical vector to factor
logic_to_factor = as.factor(hw_df$logic_vec)
prod_log_fact = logic_to_factor * (hw_df$rand_var)

#Converting logical vector to factor then numeric
logic_factor_numeric = as.numeric(logic_to_factor)
prod_log_fact_num = logic_factor_numeric * (hw_df$rand_var)
```

Trying to take the means of the converted variables indicates that you can only take the mean of a numeric variable since the output for the mean of the _prod_log_fact_ variable was '**N/A**' - similar to above. 

# Homework 1 - Problem 2

## Creating Dataframe _hwplot_df_ for Plotting
```{r}
hwplot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  logic_vec = x + y > 1,
  num_vec = as.numeric(logic_vec),
  fact_vec = as.factor(logic_vec)
)
```

### Dataframe _hwplot_df_ Description
The dataframe _hwplot_df_ includes `r nrow(hwplot_df)` observations and `r ncol(hwplot_df)` variables, including: _x_, _y_, _logic_vec_, _num_vec_, & _fact_vec_. The number of observations where the sum of _x+y=1_ is `r sum(hwplot_df$logic_vec)`. Additionally, the mean of _x_ is `r mean(hwplot_df$x)`, the median is `r median(hwplot_df$x)`, and the standard deviation is `r sd(hwplot_df$x)`.

## Scatterplot of Dataframe _hwplot_df_
```{r}

```

